\begin{thebibliography}{99}
    
    \bibitem{1} Morey, Bruce. "Generative Design Software Exploits AI to Change How New Vehicles, Equipment Are Designed." SAE Media Group (April 1, 2018). \url{https://www.mobilityengineeringtech.com/component/content/article/tohe/pub/regulars/technical-innovations/43467?r=43251}

    \bibitem{2}  Caetano, Inês. "Computational design in architecture: Defining parametric, generative, and algorithmic design." \url{https://www.sciencedirect.com/science/article/pii/S2095263520300029}
        
    \bibitem{3} McCormack, Jon. \textit{Generative Design: A P e Design: A Paradigm for Design Research}. \url{https://dl.designresearchsociety.org/cgi/viewcontent.cgi?article=2327&context=drs-conference-papers}

    \bibitem{4} Kunfeng, Wang. \textit{Generative Adversarial Networks:Introduction and Outlook}. \url{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8039016}

    \bibitem{5} Smorzhenkovn, Nikita. \textit{The use of generative design for the architectural solutions synthesis in the typical construction of residential buildings}. \url{https://www.researchgate.net/publication/352966984_The_use_of_generative_design_for_the_architectural_solutions_synthesis_in_the_typical_construction_of_residential_buildings}

    \bibitem{6} Ostwald, Michael J. \textit{Ethics and the auto-generative design process}. \url{https://www.researchgate.net/publication/232914987_Ethics_and_the_auto-generative_design_process}

    \bibitem{7} Furfero, Rocco. \textit{Generative Design: An Explorative Study}. \url{https://www.researchgate.net/profile/Rocco-Furferi/publication/341586741_Generative_Design_An_Explorative_Study/links/5ecf8379458515294518585c/Generative-Design-An-Explorative-Study.pdf}

    \bibitem{8} Stürzer, Dominik. \textit{A Short Introduction To Generative Design}. \url{https://bigrep.com/posts/generative-design/}

    \bibitem{9} Miles, Dan. \textit{What Is Generative Design, and How Can It Be Used in Manufacturing}. \url{https://redshift.autodesk.com/articles/what-is-generative-design}
    
    \bibitem{10} Pellens, Bram \textit{A Conceptual Modelling Approach for Brhavior in Virtual Environments using a Graphical Notation and Generative Design Patterns}. \url{https://researchportal.vub.be/en/publications/a-conceptual-modelling-approach-for-brhavior-in-virtual-environme}

    \bibitem{11} Luber, Stefan / Litzel Nico. \textit{Was ist ein Generative Adversarial Network (GAN)?}. \url{https://www.bigdata-insider.de/was-ist-ein-generative-adversarial-network-gan-a-999817/}

    \bibitem{12} formlabs \textit{Generative Design 101}. \url{https://formlabs.com/blog/generative-design/}

    \bibitem{13} Zwettler, Monika. \textit{Was ist ein eigentlich Generatives Design?}. \url{https://www.konstruktionspraxis.vogel.de/was-ist-eigentlich-generatives-design-a-931380/}

    \bibitem{14} Aditi. \textit{Advantages and Disadvantages of Generative Design?}. \url{https://www.infurnia.com/blog/generative-design-pros-cons}

    \bibitem{15} Archistar \textit{The Generative Design Process – The Seven Key Stages That You Need to Know About}. \url{https://www.archistar.ai/blog/the-generative-design-process-the-seven-key-stages-that-you-need-to-know-about/}

    \bibitem{16} Nicola, Pilagatti \textit{Generative Design and new designers’ role in the manufacturing industry}. \url{https://www.sciencedirect.com/science/article/pii/S2212827122011507}
    
    \bibitem{16} Ashby, M. F. \textit{How Generative Design Can Make Your Product More Sustainable}. \url{https://www.autodesk.com/autodesk-university/de/node/84137}




\end{thebibliography}